The Weakly Nonlinear Magnetorotational Instability

### 2016-08-15 paper/widegap_mri_paper.tex
changed nondim description to inner cylinder

where J is the Jacobian $J(f, g) \equiv \partial_z f \partial_r g - \partial_r f \partial_z g$. Note that in the above, $\nabla^2 f \equiv \partial_r^2 f + \partial_z^2 f + \frac{1}{r} \partial_r f$. Equations \ref{eq:Psi_perturbed} - \ref{eq:nonlinear_B} are nondimensionalized, where lengths have been scaled by $r_0$, velocities by $r_0 \Omega_0$, densities by $\rho_0$, and magnetic fields by $B_0$; where $B_0$ appears in the above it is formally unity. $\Omega_0 = \Omega(r_0)$ is the rotation rate at the center of the channel. We introduce the Reynolds number $\reye = \Omega_0 r_0^2/\nu$, the magnetic Reynolds number $\reym = \Omega_0 r_0^2 / \eta$, and a plasma beta parameter $\beta = \Omega_0^2 r_0^2 \rho_0/B_0^2$. If we define the dimensional cylindrical coordinate $r = r_0(1 + \delta x)$, the narrow gap equations are recovered in the limit $\delta \rightarrow 0$.

>>>>

where J is the Jacobian $J(f, g) \equiv \partial_z f \partial_r g - \partial_r f \partial_z g$. Note that in the above, $\nabla^2 f \equiv \partial_r^2 f + \partial_z^2 f + \frac{1}{r} \partial_r f$. Equations \ref{eq:Psi_perturbed} - \ref{eq:nonlinear_B} are nondimensionalized by inner cylinder quantities: lengths have been scaled by $r_1$, velocities by $r_1 \Omega_1$, and densities by $\rho_0$, where $\rho_0$ is the constant density. Magnetic fields are scaled by $B_0$, the constant strength of the initial background field; where $B_0$ appears in the above it is formally unity. $\Omega_1 = \Omega(r_1)$ is the rotation rate of the inner cylinder. We introduce the Reynolds number $\reye = \Omega_1 r_1^2/\nu$, the magnetic Reynolds number $\reym = \Omega_1 r_1^2 / \eta$, and a plasma beta parameter $\beta = \Omega_1^2 r_1^2 \rho_0/B_0^2$. If we define the dimensional cylindrical coordinate $r = r_1(1 + \delta x)$, the narrow gap equations are recovered in the limit $\delta \rightarrow 0$.
